---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MergedSNPs.Hsapiens.dbSNP149.GRCh38p7

<!-- badges: start -->
<!-- badges: end -->

The goal of MergedSNPs.Hsapiens.dbSNP149.GRCh38p7 is to allow an easy
translation map old SNP identifiers to its current SNP id. Note that *current*
means current as of version 149 of dbSNP (which is rather old nowadays).

This data set is based on the columns `rsHigh` (old SNP identifier) and `rsCurrent`
(new SNP identifier) from the file
[RsMergeArch.bcp.gz](ftp://ftp.ncbi.nlm.nih.gov/snp/organisms/human_9606/database/organism_data/RsMergeArch.bcp.gz).
Note that the link to this file is no longer of the version provided by this
package. To inspect the version 149 of `RsMergeArch.bcp.gz` browse into
`/data-raw/RsMergeArch.bcp.gz`.

## Installation

You can install the current version of MergedSNPs.Hsapiens.dbSNP149.GRCh38p7 with:

``` r
# install.packages("remotes")
remotes::install_github("maialab/MergedSNPs.Hsapiens.dbSNP149.GRCh38p7")
```

## Usage

Please note that the SNP identifiers should be integer numbers, and hence without the `"rs"` prefix.

```{r}
library(MergedSNPs.Hsapiens.dbSNP149.GRCh38p7)

snps <- as.numeric(253020:253050)
current_snp(snps)
```

If you rather have those SNPs that are not found in the translation table returned as `NA`, then do this instead:

```{r}
current_snp(snps, keep.orig.snp.if.not.merged = FALSE)
```
