---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MergedSNPs.Hsapiens.dbSNP149.GRCh38p7

<!-- badges: start -->
<!-- badges: end -->

The goal of MergedSNPs.Hsapiens.dbSNP149.GRCh38p7 is to allow an easy
translation map old SNP identifiers to its current SNP id. Note that *current*
means current as of version 149 of dbSNP (which is rather old nowadays).

This data set is based on the columns `rsHigh` (old SNP identifier) and `rsCurrent`
(new SNP identifier) from the file
[RsMergeArch.bcp.gz](ftp://ftp.ncbi.nlm.nih.gov/snp/organisms/human_9606/database/organism_data/RsMergeArch.bcp.gz).
Note that the link to this file is no longer of the version provided by this
package. To inspect the version 149 of `RsMergeArch.bcp.gz` browse into
`/data-raw/RsMergeArch.bcp.gz`.

## Installation

Because I use [Git LFS](https://git-lfs.github.com/) to track some of the files in this R package, you will need to have [Git LFS](https://git-lfs.github.com/) installed before installing this package. You can check if you have Git LFS already installed by running:

```bash
git lfs version
```

It should return Git LFS's version if installed, or a Git error: `git: 'lfs' is not a git command. See 'git --help'.`

If you don't have it installed already, and if you are on Ubuntu, you can install it with:

```bash
sudo apt-get update -y
sudo apt-get install -y git-lfs
```

Then, because of issues [#192](https://github.com/r-lib/remotes/issues/292), [#91584](https://community.rstudio.com/t/cant-access-data-in-a-package-that-i-created/91584), [#889](https://github.com/r-lib/devtools/issues/889), you need to clone this repository first and then install from the local folder generated on your computer:

```bash
# This will clone the repository to your home folder.
cd ~
git clone https://github.com/maialab/MergedSNPs.Hsapiens.dbSNP149.GRCh38p7
```

And finally install MergedSNPs.Hsapiens.dbSNP149.GRCh38p7 from the local folder (assuming it's in your home folder):

``` r
# install.packages("remotes")
remotes::install_local("~/MergedSNPs.Hsapiens.dbSNP149.GRCh38p7")
```

If the installation went successful, you may remove the local folder `~/MergedSNPs.Hsapiens.dbSNP149.GRCh38p7` (or other path if you cloned to another folder):

```bash
rm -rf ~/MergedSNPs.Hsapiens.dbSNP149.GRCh38p7
```

## Usage

Please note that the SNP identifiers should be integer numbers, and hence without the `"rs"` prefix.

```{r}
library(MergedSNPs.Hsapiens.dbSNP149.GRCh38p7)

snps <- as.numeric(253020:253050)
current_snp(snps)
```

If you rather have those SNPs that are not found in the translation table returned as `NA`, then do this instead:

```{r}
current_snp(snps, keep.orig.snp.if.not.merged = FALSE)
```
